Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-22 01_Meta-analysis_experiments.Rmd
Use cache dir not data for newly written files
grammar

This meta-analysis uses data collected by a number of researchers from the
Department of Agriculture and Primary Industries and the University of Southern
Queensland. It is worth noting Professor Malcolm Riley and Dr Sue Thompson's
effort in establishing and coordinating early field trials between 2010 and
2016.

@@

write.csv(experiment_sites,
          "data/Mungbean_experiment_sites.csv",
          row.names = FALSE)

>>>>

This meta-analysis uses data collected by a number of researchers from the
Department of Agriculture and Primary Industries and the University of Southern
Queensland. It is worth noting Professor Malcolm Riley's and Dr Sue Thompson's
effort in establishing and coordinating early field trials between 2010 and
2016.

@@

write.csv(experiment_sites,
          "cache/Mungbean_experiment_sites.csv",
          row.names = FALSE)
